---
title: "README: Test Reticulate package"
author: 
- Andrew Davis, PhD, Unilever Human Biology
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  rmarkdown::html_document:
    toc: TRUE
---

# Overview

This is a tutorial to practice running reticulate in RStudio.

Based on a tutorial from: https://docs.rstudio.com/tutorials/user/using-python-with-rstudio-and-reticulate/


```{bash}
source .venv/bin/activate
```

# Metadata:


# Input Data



# Analysis pipeline:



# Output:

The remaining output files were saved to the "Results" folder in this repository.

```{r, echo=FALSE}
list.files(path="Results")
```

# Mechanics

The analysis in this project proceeds by first cleaning the Results directory using 95_Make_Clean.Rmd. Then, one should run all of the code chunks in 99_Run_All.Rmd (this runs the each of the Rmd scripts in numerical sequence). The IPA analyses were run within IPA.

The Rmd scripts are as follows:

1. 1.03_Gather-and-Tidy-Data.Rmd

# Summary:




#### Need to double check: 


## Notes/To do:



### Session information

```{r session_info}
sessionInfo()
```

This document was processed on: `r Sys.Date()`.





